\section{显示引用}
想象一下你的作品中有其他作者的引用。如果只是简单的插入到
文本中的话将会使得难以阅读。一种常用的提高可读性的方式是:
设置这些文本两边缩进。
	\subsection{Time for action-quoting a scientist}
	我们将引用著名物理学家的思想。
	\begin{lstlisting}[language={[LaTeX]TeX}]
	\documentclass{article}
	\begin{document}
	Niels Bohr said: ``An expert
	is a person who has made
	all the mistakes that can be made
	in a very narrow field.''
	Albert Einstein said:
	\begin{quote}
		Anyone who has never made a mistake
		has never tried anything new.
	\end{quote}
	Errors are inevitable. So,
	let's be brave trying something new.
	\end{document}
	\end{lstlisting}
首先我们使用了行内引用。产生了一个左引号；这个字符也称作backtick。产生了个右
引号。我们只是键入两个这样的符号来获得双引号。

然后我们使用quote 环境来显示引用。我们并没有开始一个新的段落，因为引用已经
设置了缩进。这就是我们在环境中前后不使用空行的原因。
	\subsection{引用更长的文本}
当你写短的引用的时候，the quote environment 看起来非常好。然而，当你需要引用的
文本有好几段的时候，你可能会希望获得与环绕文字相通的缩进格式。The quotation
environment将会为你解决问题。
	\subsection{Time for action-quioting TeX's benefits}
\begin{lstlisting}[language={[LaTeX]TeX}]
\documentclass{article}
\usepackage{url}
\begin{document}
The authors of the CTAN team listed ten good reasons
for using \TeX. Among them are:
\begin{quotation}
	\TeX\ has the best output. What you end with,
	the symbols on the page,
	is as useable, and beautiful,
	as a non-professional can produce.
	\TeX\ knows typesetting. As those
	plain text samples
	show, \TeX's has more sophisticated
	typographical algorithms
	such as those for making paragraphs
	and for hyphenating.
	\TeX\ is fast. On today's machines
\end{quotation}
\end{document}
\end{lstlisting}
