\section{列表的嵌套}
当一个列表变长时，我们可以通过分割是它变得清晰明了。我们只是在列表中创建列表。
建议使用不同的bullet保持列表的层次清晰。LaTeX会自动这样做。
	\subsection{Tiem for action-listing packages by topic}
We shall refine the package list by introducing categories:
1. Refine the aforementioned highlighted itemize environment of our example
in the following way:
	\begin{lstlisting}[language={[LaTeX]TeX}]
	\begin{itemize}
		\item Page layout
			\begin{itemize}
				\item geometry
				\item typearea
			\end{itemize}
		\item Headers and footers
			\begin{itemize}
				\item fancyhdr
				\item scrpage2
			\end{itemize}
		\item Line spacing
			\begin{itemize}
				\item setspace
			\end{itemize}
	\end{itemize}
	\end{lstlisting}
	我们只是简单的在列表中插入了列表。最高可以嵌套四层，否则LaTeX会
	停止并输出错误信息 !LaTeX Error: Too deeply nested. 如我们所见，
	第一曾用bullet标记，第二层用英文段横线。第三曾使用星号*，第四层
	和以后的使用圆点标记。

	深度嵌套的列表着实少见；如此复杂的结构将会很难阅读。在这种情况下，
	it could be a good idea to revise the text structure or at least
	spilt the list.
\section{创建一个编号列表}
bulleted lists are useful 如果顺序不重要的话。然而，如果顺序重要的话，我们
可以给出数字创建有序列表。这将使得读者可以轻松跟着我们的思路。
	\subsection{Tiem for action-writing a step-by-step tutorial}
	让我们写个how-to并设计页面布局:
	\begin{lstlisting}[language={[LaTeX]TeX}]
	\documentclass{article}
	\begin{document}
	\begin{enumerate}
		\item State the paper size by an option to the documentclass
		\item Determine the margin dimensions using one of these packages
			\begin{itemize}
				\item geometry
				\item typearea
			\end{itemize}
		\item Customize header and footer by one of these packages:
			\begin{itemize}

